\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}

% Disable global paragraph indentation
\setlength{\parindent}{0pt}

% Custom section formatting
\newcommand{\cvsection}[1]{
    \vspace{1.5ex}
    {\noindent\textbf{\large \uppercase{#1}}}
    \vspace{0.3ex}
    \hrule
    \vspace{0.8ex}
}

% Custom list spacing for perfect indentation and ZERO top spacing
\renewenvironment{itemize}{
    \begin{list}{\textbullet}{
        \setlength{\leftmargin}{0.15in}
        \setlength{\itemsep}{1pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \setlength{\topsep}{0pt}
        \setlength{\partopsep}{0pt}
    }
}{
    \end{list}
}

% Experience entry: \cventry{Company}{Location}{Role}{Dates}
% Uses tabular* to guarantee dates are flush to the right margin.
\newcommand{\cventry}[4]{%
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & #2 \\[0pt]
    \textit{#3} & #4 \\[0pt]
  \end{tabular*}%
}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{WEI (WILLIAM) CHEN}} \\
    626-491-7382 | wchen0924@gmail.com | https://www.linkedin.com/in/weiwchen/
\end{center}

\cvsection{Education}
\textbf{UCLA Anderson School of Management} \hfill Los Angeles, CA \\
Master of Financial Engineering \hfill GPA: 3.38/4 \hfill December 2025 \\
\textit{Relevant Courses: Machine Learning, Derivatives, and Econometrics}

\vspace{0.6ex}

\textbf{The Chinese University of Hong Kong} \hfill Hong Kong \\
B.A., Insurance, Financial and Actuarial Analysis, Minor in Statistics \hfill December 2022 \\
\textit{Relevant Courses: Time Series, Deep Learning, and Non-Parametric Statistics}

\cvsection{Skills \& Professional Certifications}
\textbf{Technical Skills:} Python (NumPy, Pandas, Scikit-learn, Polars and Numba), SQL, and Git \\
\textbf{Certifications:} SOA Exam QFIQF \\
\textbf{Other Skills:} Machine Learning, Natural Language Processing, and Prompt Engineering

\cvsection{Professional Experience}
\cventry{Vertex Capital Management}{United States}{Quantitative Research Intern}{June 2025 -- September 2025}
\begin{itemize}
\item Developed a robust data pipeline to clean high-frequency option quotes, standardizing inputs for portfolio analytics, backtesting workflows, and production-ready research datasets used by stakeholders.
\item Engineered a high-performance Python backtesting framework to evaluate option strategies across large parameter grids and market regimes, accelerating iteration cycles while improving systematic strategy performance measurement.
\item Monitored and decomposed daily PnL by strategy and risk drivers, translating risk analytics into actionable insights that refined trading algorithms and improved communication with non-technical decision makers.
\end{itemize}
\vspace{0.8ex}

\cventry{Pacific Life Insurance}{Hong Kong}{Actuarial Analyst}{January 2023 -- September 2024}
\begin{itemize}
\item Developed automated pricing tools to evaluate profitability under multiple scenarios, improving operational efficiency by 50\% and creating repeatable analytics workflows for cross-functional product stakeholders.
\item Applied sensitivity and scenario analysis to quantify financial impacts of new rider features, supporting launch decisions that improved ROE by 10\% and strengthened model governance and transparency.
\item Analyzed 100K+ historical claim records to recalibrate pricing assumptions, improving valuation accuracy while strengthening data quality checks and scalable reporting for management decision making.
\end{itemize}

\cvsection{Projects}
\textbf{Voice-Based AI Financial Discord Chatbot}
\begin{itemize}
\item Architected a full-stack voice AI assistant integrating speech-to-text, local LLM inference, tool-calling APIs, and real-time text-to-speech streaming, delivering an interactive user experience with reliable workflow orchestration.
\item Deployed a local Qwen-8B model with an MCP tool interface to enable deterministic financial function calls, improving system resilience by reducing hallucination risk and enforcing structured outputs.
\item Built a low-latency audio pipeline using Librosa, VAD, and Fast-Whisper plus CUDA-accelerated TTS streaming, optimizing end-to-end responsiveness while standardizing interfaces via docstring-driven function calling.
\end{itemize}
\vspace{0.8ex}

\textbf{Implied Volatility Surface Modelling in Crypto Options}
\begin{itemize}
\item Built an end-to-end implied volatility surface system for BTC/ETH options using Deribit data (2019--2025), covering forward inference, IV extraction, and calibration across maturities for portfolio risk analytics.
\item Implemented a nanosecond-level IV solver in Rust using the J\"ackel framework, achieving 140ns runtime and 20\% speed improvement versus baseline while maintaining $<5\times 10^{-9}$ error.
\item Calibrated arbitrage-free SSVI, SVI, and B-spline surfaces with constrained optimization and regularization, improving stability under sparse strikes and volatile regimes using liquidity-aware objective functions.
\end{itemize}

\cvsection{Competitions}
\textbf{Annual IAQF Academic Affiliate Membership Student Competition}
\begin{itemize}
\item Developed a 30-day Single-Stock VIX (SSVIX) measure by incorporating additional maturities, improving risk-neutral volatility estimation reliability when near- and next-term options are illiquid.
\item Enhanced index implied correlation modeling by integrating SSVIX for the top 50 S\&P 500 constituents, providing more theoretically sound insights for correlation dynamics, tail risk, and crash risk analysis.
\item Leveraged a one-factor Student-t EGARCH model and Constant Conditional Correlation framework to simulate volatility spillovers, translating market shock scenarios into option risk analytics and portfolio implications.
\end{itemize}

\end{document}