\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}

% Disable global paragraph indentation
\setlength{\parindent}{0pt}

% Custom section formatting
\newcommand{\cvsection}[1]{
    \vspace{1.5ex}
    {\noindent\textbf{\large \uppercase{#1}}}
    \vspace{0.3ex}
    \hrule
    \vspace{0.8ex}
}

% Custom list spacing for perfect indentation and ZERO top spacing
\renewenvironment{itemize}{
    \begin{list}{\textbullet}{
        \setlength{\leftmargin}{0.15in}
        \setlength{\itemsep}{1pt}
        \setlength{\parskip}{0pt}
        \setlength{\parsep}{0pt}
        \setlength{\topsep}{0pt}
        \setlength{\partopsep}{0pt}
    }
}{
    \end{list}
}

% Experience entry: \cventry{Company}{Location}{Role}{Dates}
% Uses tabular* to guarantee dates are flush to the right margin.
\newcommand{\cventry}[4]{%
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & #2 \\[0pt]
    \textit{#3} & #4 \\[0pt]
  \end{tabular*}%
}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{WEI (WILLIAM) CHEN}} \\
    999-999-9999 | wchen0924\_NOT\_REAL@gmail.com | https://www.linkedin.com/in/weiwchen\_NOT\_REAL/
\end{center}

\cvsection{Education}
\textbf{UCBB Madison School of Management} \hfill Bar Bara, CA \\
Master of Financial Engineering \hfill GPA: 3.38/4 \hfill December 2025 \\
\textit{Relevant Courses: Time Series, Fixed-Income Markets, and Machine Learning}

\vspace{0.8ex}

\textbf{The English University of Hong Kong} \hfill Hong Kong \\
B.A., Business Administration, Minor in Statistics \hfill December 2022 \\
\textit{Relevant Courses: Non-Parametric Statistics, Time Series, and Deep Learning}

\cvsection{Skills \& Professional Certifications}
\textbf{Technical Skills:} Python (NumPy, Pandas, Scikit-learn, Polars and Numba), SQL, and Git \\
\textbf{Certifications:} SOA Exam QFIQF \\
\textbf{Other Skills:} Monte Carlo Simulation, Prompt Engineering, and Data Cleaning

\cvsection{Professional Experience}
\cventry{Proton Capital Management}{United States}{Quantitative Research Intern}{June 2025 -- September 2025}
\begin{itemize}
\item Developed a systematic screening workflow for mispriced fixed income securities using yield spread analytics across 500+ instruments, strengthening risk-aware trade selection and cross-sectional monitoring.
\item Built a Python stress-testing engine for interest-rate shocks, quantifying DV01 and convexity under parallel shifts, twists, and butterflies to support scenario-based market risk analytics.
\item Automated daily risk reporting by aggregating Greeks across the book, reducing manual runtime by 60\% while improving reproducibility and controls for time-series driven risk dashboards.
\end{itemize}
\vspace{0.8ex}

\cventry{General Life Insurance}{Hong Kong}{Actuarial Analyst}{January 2023 -- September 2024}
\begin{itemize}
\item Designed an experience-study analytics framework over 200K+ policy records, applying statistical segmentation to evaluate lapse and mortality time series for IFRS 17 assumption governance.
\item Automated model validation workflows in Python, replacing Excel-based reconciliations and reducing quarterly reporting cycle time by 40\% through repeatable data cleaning and audit-friendly outputs.
\item Built scenario projection models for product launches, quantifying capital requirements and embedded value sensitivity under stress assumptions, and translating results into stakeholder-ready documentation.
\end{itemize}

\cvsection{Projects}
\textbf{Automated Earnings Call Sentiment and Return Prediction}
\begin{itemize}
\item Built an automated ingestion pipeline using the SEC EDGAR API and spaCy parsing to process earnings-call transcripts, reducing end-to-end unstructured text processing from hours to under 10 minutes.
\item Fine-tuned FinBERT on 5,000+ transcripts to classify tone with 84\% test accuracy, then engineered sentence-level time-series signals for cross-sectional event studies.
\item Combined NLP-derived signals with earnings surprise factors using a stacking ensemble, improving predictive R\textsuperscript{2} by 22\% while keeping the feature pipeline reproducible in Python.
\end{itemize}
\vspace{0.8ex}

\textbf{Fixed Income Relative Value and Curve Trading Strategy}
\begin{itemize}
\item Constructed a PCA-based yield-curve decomposition to extract level, slope, and curvature factors, enabling systematic relative-value monitoring across 2s5s10s and butterfly structures.
\item Backtested carry-and-rolldown strategies on U.S. Treasury and swap markets (2015--2024), achieving Sharpe 0.72 gross with max drawdown of $-6.3\%$ over the full period.
\item Implemented DV01-neutral position sizing with stop-loss triggers and z-score mean-reversion filters, improving risk-adjusted returns by 25\% and reducing whipsaw trades by 35\%.
\end{itemize}

\cvsection{Competitions}
\textbf{Morgan Stanley Quant Finance Challenge 2024 (Top 10 Finalist)}
\begin{itemize}
\item Developed a dynamic delta-vega hedging strategy for a structured equity product under stochastic volatility, minimizing P\&L variance across 10,000 Monte Carlo simulation paths.
\item Designed a stress-testing framework evaluating portfolio resilience under 8 macro scenarios, including rate shocks, credit spread widening, and equity drawdowns for risk management review.
\end{itemize}

\end{document}